Visualization and analysis of probability distributions of large temporal data

### 2021-11-04 Rmd/00-c-declaration.Rmd
index and gitignore files update

@@

\textbf{Student name:} Sayani Gupta

>>>>

I hereby declare that this thesis contains no material which has been accepted for the award of any other degree or diploma at any university or equivalent institution and that, to the best of my knowledge and belief, this thesis contains no material previously published or written by another person, except where due reference is made in the text of the thesis.

This thesis includes 3 publications, two of which have been revised and resubmitted and one not yet submitted. The core theme of the thesis is "tidy tools for temporal data". The ideas, development and writing up of all the papers in the thesis were the principal responsibility of myself, the student, working within the Department of Econometrics and Business Statistics under the supervision of Professor Dianne Cook and Professor Rob J Hyndman.

The inclusion of co-authors reflects the fact that the work came from active collaboration between researchers and acknowledges input into team-based research.

In the case of Chapter 2, 3 and 4 my contribution to the work involved the following:

\begin{table}
\centering\footnotesize\tabcolsep=0.12cm
\begin{tabular}{|p{1cm}|p{2cm}|p{1.5cm}|p{3.5cm}|p{3.5cm}|p{1.5cm}|}
\hline
\RaggedRight\textbf{Thesis Chapter}  & \RaggedRight\textbf{Publication Title}  & \RaggedRight\textbf{Status (published, in press, accepted or returned for revision)}  & \RaggedRight\textbf{Nature and} {\%} \RaggedRight\textbf{of student contribution} & \RaggedRight\textbf{Co-author name(s) Nature and} {\%} \RaggedRight\textbf{of Co-author’s contribution} & \RaggedRight\textbf{Co-author(s), Monash student Y/N} \\ \hline
2 & Calendar-based graphics for visualizing people's daily schedules & Returned for revision & 70\%. Concept and developing software and writing first draft & (1) Dianne Cook, Concept and input into manuscript 20\% (2) Rob J Hyndman, input into manuscript 10\% & \multicolumn{1}{c|}{N} \\
\hline
3 & A new tidy data structure to support exploration and modeling of temporal data & Returned for revision & 80\%. Concept and developing software and writing first draft & (1) Dianne Cook, input into manuscript 15\% (2) Rob J Hyndman, input into manuscript 5\% & \multicolumn{1}{c|}{N} \\
\hline
4 & Data representation, visual and analytical techniques for demystifying temporal missing data & To be submitted & 80\%. Concept and developing software and writing first draft & (1) Dianne Cook, Concept and input into manuscript 15\% (2) Rob J Hyndman, input into manuscript 5\% & \multicolumn{1}{c|}{N} \\
\hline
\end{tabular}
\end{table}

@@

\textbf{Student name:} Yiru (Earo) Wang

### 2021-11-04 index.Rmd
index and gitignore files update

---
title: 'Visualization and analysis of probability distributions of large temporal data'
author: 'Sayani Gupta'
degreetype: 'Doctor of Philosophy'
site: bookdown::bookdown_site
degrees: 'M.Stat, B.Sc (Stat Hons)'
bibliography: [bib/gravitas.bib, bib/hakear.bib, bib/gracsr.bib, bib/thesisrefs.bib]
link-citations: yes
---

>>>>

---
title: 'Visualization and analysis of probability distributions of large temporal data'
author: 'Sayani Gupta'
degreetype: 'Doctor of Philosophy'
site: bookdown::bookdown_site
degrees: 'M.Stat, B.Sc (Stat Hons)'
bibliography: [bib/gravitas.bib, bib/tsibble.bib, bib/mists.bib, bib/thesisrefs.bib]
link-citations: yes
---
